Cheminformatics: The Computer Science of Chemical Discovery

### 2011-11-10 paper.tex
added figs back to main doc

% \begin{figure}
% \centering
% \includegraphics[height=1.3in]{platins.png}
% \caption{The generated InChI is the same for the stereoisomers cisplatin and transplatin.}
% \label{figure:cistrans}
% \end{figure}
% %
% \begin{figure}
% \centering
% \includegraphics[height=2in]{CACM_ApplicabilityDomain.pdf}
% \caption{Illustration of the ``Applicability Domain'' concept. In order to estimate whether model predictions are reliable, it is crucial to define areas of ``chemical space'' where the model is applicable, and where it is not. In this case, the ``model domain'' includes the molecule at the top. The (relatively similar) molecules to the left are likely to be included in the Applicability Domain of the model, while the (more dissimilar) molecules to the right are likely located outside this domain, hence the generated model is probably not applicable.}
% \label{figure:applicability-domain}
% \end{figure}
% %
\end{document}

>>>>

\begin{figure}
\centering
\includegraphics[height=1.3in]{platins.png}
\caption{The generated InChI is the same for the stereoisomers cisplatin and transplatin.}
\label{figure:cistrans}
\end{figure}
%
\begin{figure}
\centering
\includegraphics[height=2in]{CACM_ApplicabilityDomain.pdf}
\caption{Illustration of the ``Applicability Domain'' concept. In order to estimate whether model predictions are reliable, it is crucial to define areas of ``chemical space'' where the model is applicable, and where it is not. In this case, the ``model domain'' includes the molecule at the top. The (relatively similar) molecules to the left are likely to be included in the Applicability Domain of the model, while the (more dissimilar) molecules to the right are likely located outside this domain, hence the generated model is probably not applicable.}
\label{figure:applicability-domain}
\end{figure}
%
\end{document}
